---
title: "Split apply combine ..."
author: "Eryn Blagg"
topic: "02"
layout: post
root: ../../../
---

1. **Which (base R) functions do you know that support the split-apply-combine strategy? In your opinion, are these sufficient - state why or why not?**. 

It is a little hard for me to think of using base functions without plyr functions, as I learned R having starting with plyr and plyr functions. One of the most common uses is the  aggregate function. This function works to group data by common values of a factor and generate summary statistics/apply functions for those groups, while aggregate in base R can only apply a single named function to grouped data, the summarise function in dplyr allows for any number of functions to be specified, making it more readable, and easier to follow. I think that base R can be sufficient if you know coding well, or have a backround in using programs such as java or C, but if R is the only program that you know, I think plyr is a much better option to keep the coding clean looking and easier to read. 

2. **Using a dataset of your choice, show (by including the split-apply-combine command(s) in your answer) how you can use the split-apply-combine strategy for a part of the data analysis.**


```{r}
library(tidyverse)
```

```{r}
movie<-classdata::mojo
head(movie)
```

Using the commands in dply, we can see spefic movies and lable them, to see more specifics about your data set and individual movies or studios. 

```{r}
labe<-movie%>%
  group_by(Title, Studio)%>%
  summarise(lastWeek=min(c(max(Week), 30)), Total=`Total Gross`[Week==lastWeek][1])

movie%>%
  ggplot(aes(x=Week,y=`Total Gross`))+
  geom_line(aes(group=Title))+
  geom_text(aes(x=lastWeek, y= Total, label= Title),data=labe%>%filter(Total>5.5*10^8))+
  xlim(c(1,30))
```


```{r}
movie %>%
  filter(Studio == "WB") %>%
  group_by(Title) %>%
  top_n(1,`Total Gross`) %>%
  ungroup() %>%
  top_n(5,`Total Gross`) %>%
  ggplot(aes(x=Title,weight=`Total Gross`)) + geom_bar() + coord_flip()
```

