---
title: "Split-apply-combine..."
author: "Firstname Lastname"
topic: "02"
layout: post
root: ../../../
---

## Background:

## Prompt:


The `plyr` package has by now been replaced by other, even faster packages, but the idea of *Split, apply, combine* is as relevant as ever.

Read the paper [The Split-Apply-Combine Strategy for Data Analysis](https://www.jstatsoft.org/article/view/v040i01) by Hadley Wickham.


Write a blog post addressing the questions: 

1. **Which (base R) functions do you know that support the split-apply-combine strategy? In your opinion, are these sufficient - state why or why not?**. 

I use "with" and "split" functions to split, "lapply" to apply, and "aggregate" to combine. No, they not sufficint. I think that using other functions of plyr would be useful. 

2. **Using a dataset of your choice, show (by including the split-apply-combine command(s) in your answer) how you can use the split-apply-combine strategy for a part of the data analysis.**

```{r, data}
employee <- c('Yones','Daniel','Josh', "Meyer")
research_interest <- c("ML", "ML", "PM", "PM")
startdate <- as.Date(c('2010-11-1','2010-11-10','2010-11-10','2010-11-20'))
salary <- c(12000,10000,9000,5000)
employ.data <- data.frame(employee, research_interest, startdate,salary)
employ.data
```

```{r split}
# First, we split the count column by the spray column.
RI_by_groups <- with(employ.data, split(research_interest, groups))
RI_by_groups
```

```{r apply}
# Secondly, we apply the statistic to each element of the list. Lets use the mean here.
mean_by_salary <- lapply(salary, mean)
mean_by_salary
```

```{r combine}
# Combine date with salary
combine <- aggregate(salary ~ startdate, employ.data, mean)
combine
```




