---
title: "Split apply combine ..."
author: "Virginia Nichols"
topic: "02"
layout: post
root: ../../../
---

## What do I think of base R?
1. **Which (base R) functions do you know that support the split-apply-combine strategy? In your opinion, are these sufficient - state why or why not?**. 

subset, the family of apply functions, merge
WHile these are probably sufficient (they get the job done), I don't think they 
are desirable. I myself struggled to utilize these functions, but have found
the tidyverse functions intuitive and require less googling on my part. 

## Show me things.
2. **Using a dataset of your choice, show (by including the split-apply-combine command(s) in your answer) how you can use the split-apply-combine strategy for a part of the data analysis.**

Let's use the iris data set. Load the tidyverse!
```{r setup}
library(tidyverse)
iris <- as_tibble(iris)
head(iris)
```

What if I want to know the mean sepal length for each species?

Let's use the tidyverse for a simple example:

```{r tidyverse}
iris %>%
  group_by(Species) %>% #--split
  summarise(meanSL = mean(Sepal.Length, na.rm = T)) #--apply and combine
```

Now do the same thing in base R. First we have to figure out what the values of Species might be:

```{r base1}

str(iris)

```
Now make a subset of data for each species:
```{r base2}

iris1 <- subset(iris, Species == "setosa")
iris2 <- subset(iris, Species == "versicolor")
iris3 <- subset(iris, Species == "virginica")


```
Now calculate the mean in each subest
```{r base3}

iris1.mean <- mean(iris1$Sepal.Length)
iris2.mean <- mean(iris2$Sepal.Length)
iris3.mean <- mean(iris3$Sepal.Length)

```
Now combine the information
```{r base4}

iris.means <- data.frame( species = c("setosa", "versicolor", "virginica"),
                          meanSL = c(iris1.mean, iris2.mean, iris3.mean))
iris.means
```
Yuck. Thanks Hadley Wickham!