---
title: "Split-apply-combine..."
author: "Min Zhang"
topic: "02"
layout: post
root: ../../../
---

The `plyr` package has by now been replaced by other, even faster packages, but the idea of *Split, apply, combine* is as relevant as ever.

Read the paper [The Split-Apply-Combine Strategy for Data Analysis](https://www.jstatsoft.org/article/view/v040i01) by Hadley Wickham.


Write a blog post addressing the questions: 

1. **Which (base R) functions do you know that support the split-apply-combine strategy? In your opinion, are these sufficient - state why or why not?**. 

Base R functions that support split-apply-combine strategy include `aggregate()` and `apply()` family. They are not sufficient compared with `dplyr` package, due to readability and number of functions to apply. 

2. **Using a dataset of your choice, show (by including the split-apply-combine command(s) in your answer) how you can use the split-apply-combine strategy for a part of the data analysis.**

The dataset I use for illustration is `mtcars`. The task is to obtain the mean mpg (miles per gallon) and its variance. 

```{r, include=FALSE}
library(MASS)
library(dplyr)
```

**a. with `aggregate()`**
```{r}
aggregate(mtcars[, "mpg"], list(cyl = mtcars$cyl), mean)
aggregate(mtcars[, "mpg"], list(cyl = mtcars$cyl), var)
```

**b. with `dplyr`** It's easier to read thanks to the %>% operator, and I can do multiple commands in one `summarise()`.
```{r}
mtcars %>% group_by(cyl) %>% 
  summarise(mpg.mean = mean(mpg), mpg.var = var(mpg))
```

