---
title: "Interesting times"
author: "Gulzina Kuttubekova"
root: ../../../
layout: post
topic: '04'
---


1. **Describe what intervals, durations, periods, and instants are, and give one example for each that shows why we need these distinctions.**

- Instant: is an infinitesimal measure of the moment of time. It is a specific moment in timem like: now, today, etc.
What is the time right now -- instant:
```{r}
now() #returns time in hours, minutes and seconds as well as the today's date
```

- Duration: is the amount of time elapsed between two events. Events might be measured in different ways: centuries, years, months, weeks, hours, minutes, second or even milliseconds. Depending on the case, one may choose a specific measurement. However, it may cause difficulties (eg. in DS research). To avoid this, we can utilize lubridate’s approach: duration measurement in seconds.

Calculate the duration of the STAT585 class:
```{r, include = FALSE}
library(dplyr)
library(lubridate)
library(ggplot2)
```

```{r}
dhours(x = 5.5 - 4.167) #seconds
```

- Period: is also a time span, but compared to duration it does not have fixed length in seconds. It’s rather a “human” measure of time, rather than physical (scientific). A period may represent a day, month, year, hour or even their linear combination. It is most useful in dealing with timezone conflicts.

Create a new period consisting of 28 days:
```{r}
w_cycle <- days(28)
w_cycle #this data structure probably is used in mobile App: flo
```

- Interval: is time span with a starting and ending point. It is similar to duration but is used for more “human” measure of time. If one wants to obtain how many periods were in a specific time span, it is better to use interval rather than duration. It is also helpful in dealing with leap years/seconds. 

Calculate how many cycles a woman has on average in one year:
```{r}
next_year <- today() + years(1)
(today () %--% next_year) / w_cycle #on average 13 cycles
```

2. **The `ggplot2` package works seamlessy with lubridate. Find a data set with dates and/or times, use lubridate to work with the dates/times, then plot a time-related aspect of the data and describe it.**

 I chose lakers data from the lubridate package. 
```{r}
# first take a look at the dataset
lakers %>% glimpse
```

We see that "date" variables is recorded as integer, so we have to convert it to date data type:
```{r}
lakers %>% mutate_at(1, ymd) -> new_lakers 
# integer is parsed into year-month-day
class(new_lakers$date) #date ds, not integer
```

We can make new variables such day, month and year separate from date variable. Those variables will be stored as integers:
```{r}
new_lakers %>% filter(team == "LAL") %>% group_by(date) %>%  mutate(year = year(date), month = month(date), day = day(date), score = sum(points)) -> lal_lakers
```

Some fun plots:
- We see that there were almost no games in November and December.
```{r}
# frequency of played games 
lal_lakers %>% group_by(date) %>% ggplot(aes(date)) + geom_freqpoly(binwidth = 2)
```

LA team scored more mostly when they were playing at home. Interestingly they scored more away from late January to mid February.
```{r}
lal_lakers %>% ggplot(aes(x = date, y = score, col = game_type)) + geom_line(linejoin = "round")
```








