---
title: "Interesting times..."
author: "Qing He"
topic: "04"
layout: post
root: ../../../
---


## Background:

Dates and times can be difficult to work with. Watch [this video](https://www.youtube.com/watch?v=-5wpm-gesOY) to appreciate all of the fun scenarios that date/time libraries have to accommodate. 

Luckily, the `lubridate` package makes working with dates and times in R pretty straightforward. The package has been described in the paper [Working with date and time](http://www.jstatsoft.org/v40/i03/) by Garrett Grolemund and Hadley Wickham, an updated version of an intro to lubridate can be found in chapter 16 of [R for Data Science](https://r4ds.had.co.nz/dates-and-times.html). Read one of the two sources.

Write a blog post addressing the questions:


- Describe what intervals, durations, periods, and instants are, and give one example for each that shows why we need these distinctions.
###Intervals: represent a starting and ending point.
It can be helpful when finding out how many days are contained in one specific year.
```{r}
library(lubridate)
#An estimate of how many days in a year
years(1) / days(1)
#find out how many days in this year
next_year <- today() + years(1)
(today() %--% next_year) / ddays(1)
```

###Durations: number of seconds.
It is straight forward to add, subtract, multiply with time represented as intervals.
```{r warning=FALSE}
2 * dyears(1)
dyears(1) + dweeks(12) + dhours(15)
tomorrow <- today() + ddays(1)
last_year <- today() - dyears(1)
```
###Periods: human units like weeks and months.
Avoid the problems caused by calculating non-standard human time unit such as days that are not 24 hours due to the time zone.
```{r}

one_pm <- ymd_hms("2016-03-12 13:00:00", tz = "America/New_York")
one_pm

#wrong result using duration
one_pm + ddays(1)

#correct result using period
one_pm + days(1)
```
###Instants: the specific time point, a date, a time within a day or a date-time. 
It show the time piont in a formated way.
```{r}
today()
now()
```

- The `ggplot2` package works seamlessy with lubridate. Find a data set with dates and/or times, use lubridate to work with the dates/times, then plot a time-related aspect of the data and describe it.  
Plot the shotting attempt made by Kobe Bryant from 2008 to 2009, facet by shot that been missed and made for every 7 days. Date been converted to time instant and ploted with ggplot.
```{r message=FALSE, warning=FALSE}
library(tidyverse)
attach(lakers)
str(lakers)
lakers %>% 
  filter(player=="Kobe Bryant", etype=="shot") %>% 
  ggplot(aes(ymd(date),fill=result))+
  geom_histogram(binwidth = 7)+ facet_grid(result~.)
  

```



