---
title: "Interesting times..."
author: "Zahra Khoshmanesh"
topic: "04"
layout: post
root: ../../../
---


##  Describe what intervals, durations, periods, and instants are, and give one example for each that shows why we need these distinctions.

  * intervals, which represent a starting (instant) and ending point. since we have 2 exact points in date/time, 
      we are able to calculate the interval by using period and duration.
  
    * example: you can start practicing for an exam in May,10 2019 at 12:00:00 pm and end in May,11 2019 at 12:00:00 pm
    
  * durations, which represent an exact number of seconds. Durations represent an exact number of seconds.
  
    * example: the duration of writing my blog #3 was 120*360 seconds.
    
  * periods, which represent human units like weeks and months. Periods are time spans but don’t have a fixed length in seconds, 
      instead they work with “human” times, like days and months.
  
    * example: June has 30 days while July has 31 days. February has 28 days except for leap years when it has 29 days.
      With the Period class, we can add 1 month to February 1 and get March 1.
  
  * instants, a specific date-time point  
  
    * example:the date and time of your birthday like 2011-12-29 at 12:33:00 pm.

##  The `ggplot2` package works seamlessy with lubridate. Find a data set with dates and/or times, use lubridate to work with the dates/times, then plot a time-related aspect of the data and describe it. 

   I am going to create a heatmap of 911 dataset[1]. We use lubricate to extract time ,hour and weekday of time stamps and 
    plot a heat map of weekday and hour.

```{r}
#installing  packages

#install.packages("plyr")
#install.packages("ggplot2")
#install.packages("dplyr")
#install.packages("lubricate")

#loading packages
library(plyr)
library(ggplot2)
library(dplyr)
library(lubridate)

```


#### read data

```{r}
#read 911 data
#reading the data
# data from githup repository
fn <- "https://raw.githubusercontent.com/shoaibb/911-Calls-Data-Analysis/master/911.csv"
download.file(fn,destfile="short911.csv")
#read csv
call911<- read.csv("short911.csv")
#checking the data 
head(call911)
```

#### Extracting hour and weekday from the datetime column

```{r}
#extracting hour from the timestamp column
call911$hour<- hour(call911$timeStamp)

#extracting weekday from the timestamp column
call911$weekday<- weekdays.POSIXt(as.Date(call911$timeStamp))

```

#### Finding the number of calls of Weekday and hour pair

```{r}

#Finding the count of hour and weekday pair using aggregate function
heatmap <- aggregate(e~ hour+weekday, data= call911, length)

```

#### Plot heatmap
```{r}
#basic background
plot <- ggplot(data = heatmap, aes(x=weekday, y=hour, fill=e,label= e))
plot
#adding layer
plot_tile <- plot + geom_tile()
plot_tile
#adding color
plot_fill_color <- plot_tile + scale_fill_gradient2(low = "#98FB98",high ="#006400")
plot_fill_color
```

### References
  1- https://www.analytics-tuts.com/correlation-matrix-heatmap-r/
  2- https://r4ds.had.co.nz/dates-and-times.html






