---
title: "Interesting times..."
author: "Virginia Nichols"
topic: "04"
layout: post
root: ../../../
---


#Describe what intervals, durations, periods, and instants are, and give one example for each that shows why we need these distinctions.

Interesting.

**Durations** represent exact number of seconds. To convert to larger units, they use a standard convertion rate.  
*How long can I hold my breath?*
I want to know the exact amount of seconds. Whether it is a leap year is irrelevant. 

**Periods** are human units (weeks/months) 
*How many months does it take you to write a paper?*
This is not an exact value, but rather a general value that is best represented in month chunks. 

**Intervals** have a starting and ending point and operate in human units. 
*How long is the spring semester?*
It starts on Jan X and ends on May X. 

#The `ggplot2` package works seamlessy with lubridate. Find a data set with dates and/or times, use lubridate to work with the dates/times, then plot a time-related aspect of the data and describe it.**  

We'll do the typical one - NYC flights. 
```{r dates dataset, echo=FALSE, include = FALSE}
library(tidyverse)
library(lubridate)
library(nycflights13)
```
```{r look at flights}
dat <- flights
head(flights)
names(flights)
```

Yuck. It has lots of *date-y* things. Let's see if any origins have become more popular by month

```{r time plot}
flights %>%
  group_by(month, origin) %>%
  summarise(n = n()) %>%
  ggplot(aes(month, n)) + 
  geom_line(aes(color = origin))

```

The months are labeled weird, I'd rather have the words. 

```{r time plot 2}

flights %>%
  mutate(month2 = month(month, label = T)) %>%
  group_by(month2, origin) %>%
  summarise(n = n()) %>%
  
  ggplot(aes(month2, n)) + 
  geom_point(aes(color = origin))

```

But now it won't connect them with a line. Oh well. At least they are in the right order. 

