---
title: "Interesting times..."
author: "Yuchen Wang"
topic: "04"
layout: post
root: ../../../
---

- Describe what intervals, durations, periods, and instants are, and give one example for each that shows why we need these distinctions.
-Instant: a specific time
```{r message=FALSE, warning=FALSE}
library(lubridate)
library(tidyverse)
example_instant <- ymd_hms("2019-01-01 18:00:00")
is.instant(example_instant)
```

-Intervals: the time between two specific times.
```{r}
example_interval <- ymd_hms("2019-02-01 17:00:00") - ymd_hms("2019-01-01 18:00:00")
example_instant + example_interval
```

-Durations: time span (interval) in specific unit "seconds".
```{r}
example_duration <- as.duration(example_interval)
example_duration
```

-Periods: time span (interval) in other units which are larger than seconds.
```{r}
example_period <- as.period(example_interval)
example_period
```


- The `ggplot2` package works seamlessy with lubridate. Find a data set with dates and/or times, use lubridate to work with the dates/times, then plot a time-related aspect of the data and describe it.  
```{r}
ames_weather <- read_csv("https://raw.githubusercontent.com/Stat585-at-ISU/materials-2019/master/data/Ames_weather_2017-2018.csv")
ames_weather <- ames_weather %>%
  na.omit() %>%
  mutate(date = ymd(date),
         year = year(date),
         month = month(date),
         day = day(date))

ames_18 <-ames_weather %>%
  filter(year == 2018) %>%
  filter(weather == "Clear.") %>% 
  group_by(month) %>%
  summarize(
        count = n(),
        mean_wind = mean (wind))
ames_18 %>%
  ggplot(aes(x=as.factor(month),y=mean_wind,size = count,color = count)) + geom_point(position = "dodge") + labs (title = "Clear Days in 2018", x = "Month", y = "MeanWind" ) 
```
It looks like there is no relationship between the mean wind speed and the amount of clear days in every month.

