---
title: "Interesting times..."
author: "Zhenzhen Chen"
topic: "04"
layout: post
root: ../../../
---


Write a blog post addressing the questions:


- Describe what intervals, durations, periods, and instants are, and give one example for each that shows why we need these distinctions.

Intervals, durations, periods, and instants are the four time related objecteds in lubridate.

Instants shows you a specific moment in time, for example,
```{r}
library(lubridate)
tim <- now()
tim
is.instant(tim)
```

Intervals is the simplest one to shows a timespan. It can tell you exact the length of time. For example, since we already know the instants, we can calculate the interval between two or more instants. 
```{r}
tim1 <- now()
tim2 <- ymd_hms("2019.2.14 12:00:00")
sp   <- tim2 - tim1
sp
```
Duration is fixed, it isn't change. We have exact length for each seconds, since duration is measured in seconds. 
```{r}
dseconds(50)
dminutes(50)
ddays(2)
```
Since we already know interval, we can also added and subtracted interval to duration, for example,
```{r}
now() + ddays(108)
tim2 - dyears(1)
```
Periods records a timespan that larger than the unit in seconds, for example, miuntes, days, months, years. Period not like duration, it is no longer has invariable length. Be specific,
```{r}
years(1)
months(2)
years(1) + months(2)
```
We can added instants, intervals, and period to one period, but we can not added duration. The following last line shows error messgae, since we add period to duration. 
```{r}
years(1) + tim2
years(1) + dminutes(1)
```


- The `ggplot2` package works seamlessy with lubridate. Find a data set with dates and/or times, use lubridate to work with the dates/times, then plot a time-related aspect of the data and describe it. 

The data set I found is R buil-din dataset which calls "Death". It recorded the monthly deaths from bronchitis, emphysema, and asthma in the United Kingdom from 1974-1979. 
```{r, message=F}
library(lubridate)
library(ggplot2)
library(tidyverse)
##install.packages(ggfortify)
##install.packages(zoo)
library(ggfortify)
library(zoo)

data1 <- fortify(deaths)

data1 %>%
  mutate(yearmd = ymd(Index), month = month(Index)) %>%
  ggplot( aes(x = yearmd, y = Data)) + 
  geom_line() + 
  geom_smooth(method = "auto")+
  xlab("Year") +
  ylab("Death") + 
  theme_bw()
```
Based on the result, we can tell these five years(from 1974 to 1979), the death number from these lung diseases has decreased. However, for each year, we can also see that Jan and Feb are the two months which has the highest death occurrence. May and Jun have the lowest death occurrence because of lung diseases. 

