---
title: "A Series of Tubes..."
author: "Zerui Zhang"
topic: "09"
layout: post
root: ../../../
output: 
  html_document: 
    css: extra.css
---

**Write a blog post answering the following questions and detailing the progress: **

1. The `xml2` R package can be used to work with xml files. Write a function, `current_weather` that accepts a 4-letter airport code (KAMW in the URL here: https://w1.weather.gov/xml/current_obs/KAMW.xml) and returns a data frame with the airport location (station ID, latitude, longitude), last update time, and current weather information (temperature, weather condition, wind speed and direction) at that airport. The `xml2` functions `read_xml`, `xml_children`, `xml_name`, and `xml_text` will be useful. Remember to handle errors and check inputs, and make sure to return a data frame with appropriate data types. 

```{r, message=FALSE}
library(tidyverse)
library(xml2)
library(assertthat)
current_weather <- function(code){
  ids <- read_xml("https://w1.weather.gov/xml/current_obs/index.xml")
  all_codes <- xml_find_all(ids, ".//station_id") %>% xml_text()
  assert_that(is.character(code), nchar(code)==4, msg="Code is not a 4-letter character")
  if(!(code %in% all_codes)){
    stop("Code is invalid.")
  }
  xml <- paste0("https://w1.weather.gov/xml/current_obs/", code, ".xml") %>% read_xml()
  node <- xml %>% xml_children()
  names <- node %>% xml_name()
  texts <- node %>% xml_text()
  index <- which(names %in% c("station_id", 
                                  "latitude", 
                                  "longitude", 
                                  "observation_time",
                                  "weather", 
                                  "temperature_string", 
                                  "wind_dir", 
                                  "wind_mph"))
  df <- cbind(names[index], texts[index]) %>% as.data.frame()
  colnames(df) <- c("category", "information")
  checkmate::checkDataFrame(df)
  df
}
current_weather("KAMW")
```


2. Which HTML tags did you investigate? Describe how to format at least 3 separate pieces of a document using HTML tags.

Color:

<!--html_preserve-->
<h1 style="background-color:rgb(131, 116, 196); color:rgb(238, 130, 238);">Once upon a time, a princess named Hello World...</h1>
<!--/html_preserve-->

Link:

<!--html_preserve-->
<style>
a:link, a:visited {
  background-color: #f44336;
  color: white;
  padding: 15px 25px;
  text-align: center;
  text-decoration: none;
  display: inline-block;
}

a:hover, a:active {
  background-color: orange;
}
</style>

<a href="https://en.wikipedia.org/wiki/Harry_Potter" target="_blank">Harry Potter's wiki</a>
<!--/html_preserve-->


List:


<!--html_preserve-->
<html>
<body>

<p>Choose something to eat</p>
<ul style="list-style-type:circle;">
  <li>Thai curry</li>
    <ul>
      <li>Chicken</li>
      <li>Seafood</li>
    </ul>
  <li>Sweet and Sour Tofu</li>
  <li>Broccoli</li>
</ul>  

</body>
</html>
<!--/html_preserve-->


3. Compile this Rmarkdown document to HTML, then open the HTML file in a web browser. Open the inspector console for your browser (Ctrl-Shift-I in Chrome, Ctrl-Shift-C in Firefox) and look at the HTML code corresponding to various parts of the document. <br>
Answer the following questions:
    - What types of tags did you find? 
    
    Tags for color, line, block, e.g.,*head*, *body*, *style*, *div*, *p*, *ol*, *pre*, etc.
    
    - How are code chunks formatted in HTML?
    
    The code is embedded in the tag *pre class="r"*.
    
    - What differences are there in the HTML markup for R code chunks and R output blocks?
    
    The code chunks have the tag *pre class="r"*, while the output blocks have the tag *pre*.
    
    
    
4. In R, the `rvest` package, which is part of the tidyverse, makes it (relatively) easy to pull specific pieces from structured documents. The `html_nodes` function selects nodes using either xpath or css, and additional functions such as `html_attrs`, `html_text`, and `html_table` pull information out of the markup text.<br>
Choose a Wikipedia page that has at least one image to test the `rvest` package out
Remember, just because you have the HTML file doesn't mean you should commit it to your git repository!!! Delete the HTML file now if you're going to be tempted to accidentally commit and push it.

```{r, message=F, warning=F}
library(rvest)

web <- read_html("https://en.wikipedia.org/wiki/Harry_Potter")
table <- web %>% 
  html_table(fill=T, header = T) %>%
  .[[1]]
table %>% pander::pander()

img <- web %>% 
  html_nodes("#mw-content-text > div > div:nth-child(168) > div > a > img") %>% 
  html_attr("srcset") %>% 
  strsplit(" ") %>% 
  .[[1]] %>%
  .[3] %>% 
  paste0("https:",.) %>% 
  magick::image_read()
img
```