---
title: "A Series of Tubes..."
author: "Firstname Lastname"
topic: "09"
layout: post
root: ../../../
output: 
  html_document: 
    css: extra.css
---


the function
```{r echo=TRUE, message=FALSE, warning=FALSE}
library(xml2)

current_weather <- function(url){
  xmlhead <-xml2::read_xml(url)
  long = NULL 
  for (i in 7:20){
    xmlname <- xml_children(xmlhead)[i] %>% xml_name 
    xmltext <- xml_children(xmlhead)[i] %>% xml_text
    weather.df <- data.frame(xmlname, xmltext)
    long=rbind(long,weather.df)
  }
  long
  }
```

the dataframe result
```{r echo=TRUE, warning=FALSE}
amesweather <- "https://w1.weather.gov/xml/current_obs/KAMW.xml"
current_weather(amesweather)
```


2. test out the html tags
headings use h1, h2, h3, and so on, css=h1 span  
images use img, css= a img  
table use css=div table  
  
use `read_html` to read the url, then use `html_nodes` to collect out the components then use `html_text` to parse out just the text of interest



3.
a. `<code> </code>, <pre> </pre>, <div> </div>`
b. together for one chunk to appear as customized, based on how it is desired to look like 
c. xml code chunks are more free and customizable based on coffee. html code chunks more geared towards public showing, not specific templates
'
4. rvest 
```{r echo=TRUE, message=FALSE,  warning=FALSE}
library(tidyverse)
library(rvest)

breadfruit <- read_html("https://en.wikipedia.org/wiki/Breadfruit") 
h2<- breadfruit %>% html_nodes("h2 span") %>%  html_text
h2
```


```{r echo=TRUE, message=FALSE, warning=FALSE, results='hide'}
h2a<- h2 %>% subset(h2!="[edit]")
h2b<- h2a %>% subset(h2a!="[")
h2c<- h2b %>% subset(h2b!="]")
```

```{r}
h2c
```



**Write a blog post answering the following questions and detailing the progress: **
1. The `xml2` R package can be used to work with xml files. Write a function, `current_weather` that accepts a 4-letter airport code (KAMW in the URL here: https://w1.weather.gov/xml/current_obs/KAMW.xml) and returns a data frame with the airport location (station ID, latitude, longitude), last update time, and current weather information (temperature, weather condition, wind speed and direction) at that airport. The `xml2` functions `read_xml`, `xml_children`, `xml_name`, and `xml_text` will be useful. Remember to handle errors and check inputs, and make sure to return a data frame with appropriate data types. 
2. Which HTML tags did you investigate? Describe how to format at least 3 separate pieces of a document using HTML tags.
3. Compile this Rmarkdown document to HTML, then open the HTML file in a web browser. Open the inspector console for your browser (Ctrl-Shift-I in Chrome, Ctrl-Shift-C in Firefox) and look at the HTML code corresponding to various parts of the document. <br>
Answer the following questions:
    - What types of tags did you find? 
    - How are code chunks formatted in HTML?
    - What differences are there in the HTML markup for R code chunks and R output blocks?
4. In R, the `rvest` package, which is part of the tidyverse, makes it (relatively) easy to pull specific pieces from structured documents. The `html_nodes` function selects nodes using either xpath or css, and additional functions such as `html_attrs`, `html_text`, and `html_table` pull information out of the markup text.<br>
Choose a Wikipedia page that has at least one image to test the `rvest` package out
Remember, just because you have the HTML file doesn't mean you should commit it to your git repository!!! Delete the HTML file now if you're going to be tempted to accidentally commit and push it.
