---
title: "A Series of Tubes..."
author: "Gani Agadilov"
output:
  html_document:
    css: extra.css
  pdf_document: default
root: ../../../
layout: post
topic: 09
---

**Write a blog post answering the following questions and detailing the progress: **

1. The `xml2` R package can be used to work with xml files. Write a function, `current_weather` that accepts a 4-letter airport code (KAMW in the URL here: https://w1.weather.gov/xml/current_obs/KAMW.xml) and returns a data frame with the airport location (station ID, latitude, longitude), last update time, and current weather information (temperature, weather condition, wind speed and direction) at that airport. The `xml2` functions `read_xml`, `xml_children`, `xml_name`, and `xml_text` will be useful. Remember to handle errors and check inputs, and make sure to return a data frame with appropriate data types. 

```{r,warning=FALSE}
library(xml2)
library(assertthat)
library(rvest)
library(tidyverse)
library(dplyr)

current_weather <- function(code){
  checkmate::assertCharacter(code)
  
  link <- read_xml(paste0("https://w1.weather.gov/xml/current_obs/",code,".xml"))
  col <- xml_contents(link)%>%xml_name()  
  info <- link %>% xml_children() %>% xml_text
  dataframe <- as.data.frame(matrix(info, ncol  = length(info), byrow = T), stringsAsFactors = F)
  colnames(dataframe) <- col
  data <- dataframe %>% dplyr::select(station_id, latitude, longitude,
                                      observation_time,
                                      temperature_string, weather,wind_mph, wind_dir)
  return(data)
}
check <- current_weather("KAMW")
t(check)
```

2. Which HTML tags did you investigate? Describe how to format at least 3 separate pieces of a document using HTML tags.

I investigated the tags for hyperlink, table and paragraph. The hyperlink a is used to link from one page to another and href attribute indicates the link's destination. The p tag identifies a paragraph. The table tag defines an HTML table. The tr element identify a table row, the th element provides a table header, and the td element specifies a table cell.

There are examples:

Link for my website
<a href="https://ganiagadil.github.io/">  My website </a>

Table for salaries
<!DOCTYPE html>
<html>
<head>
<style>
table, th, td {
  border: 1px solid black;
}
</style>
</head>
<body>
<table>
  <tr>
    <th>Year</th>
    <th>Salary</th>
  </tr>
  <tr>
    <td>2018</td>
    <td>$50000</td>
  </tr>
  <tr>
    <td>2019</td>
    <td>$60000</td>
  </tr>
</table>

</body>
</html>

Paragraph
<!DOCTYPE html>
<html>
<body>

<p>Introduction.</p>
<p>Data analysis.</p>
<p>Conclusion.</p>

</body>
</html>

3. Compile this Rmarkdown document to HTML, then open the HTML file in a web browser. Open the inspector console for your browser (Ctrl-Shift-I in Chrome, Ctrl-Shift-C in Firefox) and look at the HTML code corresponding to various parts of the document. <br>
Answer the following questions:

    - What types of tags did you find? 
  I found tags for paragraph in console section.

    - How are code chunks formatted in HTML?
  The R code formatted in pre class="r".

    - What differences are there in the HTML markup for R code chunks and R output blocks?
  The main difference is the R code formatted in pre class="r", but R output is formatted
  in pre and class="hljs" tag.

4. In R, the `rvest` package, which is part of the tidyverse, makes it (relatively) easy to pull specific pieces from structured documents. The `html_nodes` function selects nodes using either xpath or css, and additional functions such as `html_attrs`, `html_text`, and `html_table` pull information out of the markup text.<br>
Choose a Wikipedia page that has at least one image to test the `rvest` package out

```{r,warning=FALSE}
library(tidyverse)
library(rvest)

eagle <- read_html("https://en.wikipedia.org/wiki/Golden_eagle")  

eagle %>% html_nodes("title") %>% html_text()

image <- eagle %>%  html_nodes("meta") %>% html_attrs() 

magick::image_read(image[[7]][[2]])

eagle %>% html_nodes("table") %>% html_table()
```



