---
title: "A Series of Tubes..."
author: "Yawei Ge"
topic: "09"
layout: post
root: ../../../
output: 
  html_document: 
    css: extra.css
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE,
                      message =FALSE)
```

##1. Weather Function

Sorry for the long variable names
```{r}
library(tidyverse)
library(rvest)
library(xml2)

weather_today <- function(code){
  
  #input check
  if(length(code) > 1) stop("can't accept vector")
  
  #read the xml
  xmlurl <- paste0("https://w1.weather.gov/xml/current_obs/", code, ".xml")
  
  weather <- tryCatch(read_xml(xmlurl), 
                      error = function(c) "error")
  
  if(identical(weather, "error")) stop("invaid input, please check the code")
  
  temp2 <- xml_children(weather)
  name <- xml_name(temp2)
  
  #select the useful information
  searchlist <- c("location", "station_id", "latitude", "longitude",
                  "observation_time", "temp_f", "temp_c", "weather", 
                  "wind_mph", "wind_dir")
  usedinformation <- temp2[which(name %in% searchlist)]
  
  #construct a data.frame
  usedname <- xml_name(usedinformation)
  if(!all(searchlist %in% usedname)) warning("some information not avilable")
  
  usedcontent <- as.character(xml_contents(usedinformation))
  usedcontent <- as.data.frame(t(usedcontent), stringsAsFactors = F)
  colnames(usedcontent) <- usedname
  
  #fix the output type
  usedcontent$latitude <- as.numeric(usedcontent$latitude)
  usedcontent$longitude <- as.numeric(usedcontent$longitude)
  usedcontent$temp_f <- as.numeric(usedcontent$temp_f)
  usedcontent$temp_c <- as.numeric(usedcontent$temp_c)
  usedcontent$wind_mph <- as.numeric(usedcontent$wind_mph)
  usedcontent$observation_time <- lubridate::mdy_hm(usedcontent$observation_time)
  
  return(usedcontent)
}

```

```{r, eval=FALSE}
# check the function with the following code
# this function depends on "xml2", I assumed it is attached

weather_today(c("KAAA", "KAMW"))
weather_today("ABC")
```

```{r}
str(weather_today("KAMW"))
```

##2. Which HTML tags did you investigate? Describe how to format at least 3 separate pieces of a document using HTML tags.

I investigated the *\<head\>*, *\<body\>* and *\<p\>* tags. 

If you want to have 3 separate paragraphs, you need three *\<p\>* and *\</p\>* pairs for each paragraph. If you want to have 3 separate patches, you may want three *\<div\>* and *\</div\>* pairs for each of them.

##3. In my html file

I found *\<html\>*, *\<head\>*, *\<body\>*, *\<div\>*, *\<pre\>*, *\<h1\>*, *\<h4\>*, *\<code\>*, and *\<style\>*.

The code chunk is within a *\<div\>* tag with title as *id* and heading, then it is within *\<pre\>* and *\<code\>* tags.


##4. `rvest` package 

link:<https://en.wikipedia.org/wiki/Iowa_State_University>

```{r}
isu <- read_html("https://en.wikipedia.org/wiki/Iowa_State_University")

isu_text <- isu %>%
html_nodes("#mw-content-text") %>%
html_nodes("div:first-child") %>%
html_nodes("p:nth-child(3)") %>%
html_text()

isu_text

```











