---
title: "A Series of Tubes..."
author: "Jing Hou"
topic: "09"
layout: post
root: ../../../
output: 
  html_document: 
    css: extra.css
---

**Write a blog post answering the following questions and detailing the progress: **

1. The `xml2` R package can be used to work with xml files. Write a function, `current_weather` that accepts a 4-letter airport code (KAMW in the URL here: https://w1.weather.gov/xml/current_obs/KAMW.xml) and returns a data frame with the airport location (station ID, latitude, longitude), last update time, and current weather information (temperature, weather condition, wind speed and direction) at that airport. The `xml2` functions `read_xml`, `xml_children`, `xml_name`, and `xml_text` will be useful. Remember to handle errors and check inputs, and make sure to return a data frame with appropriate data types. 

```{r message=FALSE}
library(xml2)
library(tidyverse)

current_weather <- function(code){
  assertthat::assert_that(is.character(code), nchar(code)==4)
  weather <- read_xml(paste0("https://w1.weather.gov/xml/current_obs/",code,".xml"))
  data <- weather %>% xml_children() %>%
          xml_text() %>%
          as.data.frame()
  rownames(data) <- weather %>% xml_children() %>%
          xml_name() %>%
          as.character()
  ind <- c("station_id","latitude","longitude","observation_time",
            "weather","temperature_string","wind_dir","wind_mph")
  new <- as.data.frame(data[ind,])
  colnames(new) <- NULL
  rownames(new) <- ind
  checkmate::checkDataFrame(new)
  return(new)
}

current_weather("KAMW")
```

2. Which HTML tags did you investigate? Describe how to format at least 3 separate pieces of a document using HTML tags.

I investigated headings, paragraphs, colors, links, images, and so on. 

*Headings*
<h1>Winter is coming!</h1>
*color*
<h1 style="background-color:rgb(60, 179, 113);">Winter is coming!</h1>
*link*
<a href="https://en.wikipedia.org/wiki/Winter_Is_Coming"> Winter Is Coming</a>

3. Compile this Rmarkdown document to HTML, then open the HTML file in a web browser. Open the inspector console for your browser (Ctrl-Shift-I in Chrome, Ctrl-Shift-C in Firefox) and look at the HTML code corresponding to various parts of the document. <br>
Answer the following questions:

    - What types of tags did you find?
    
    I found html, head, body, div, style, script, p, ol, and so on.

    - How are code chunks formatted in HTML?
    
    The code chunks are formatted with the start tag {pre class="r"} and the end tag {/pre}, with the code inserted in between. The start tag of the code is {code class="hljs"} and the end tag is {/code}.
    
    - What differences are there in the HTML markup for R code chunks and R output blocks?
    
    The difference is the format of the start tag {pre}. There is no {class="r"} in the start tag.
    
4. In R, the `rvest` package, which is part of the tidyverse, makes it (relatively) easy to pull specific pieces from structured documents. The `html_nodes` function selects nodes using either xpath or css, and additional functions such as `html_attrs`, `html_text`, and `html_table` pull information out of the markup text.<br>
Choose a Wikipedia page that has at least one image to test the `rvest` package out

```{r message=FALSE}
library(rvest)
library(magrittr)

game<-read_html("https://en.wikipedia.org/wiki/Winter_Is_Coming")
image<-html_nodes(game,"img") %>% 
  xml_attr(attr="src") %>%
  paste0("https:",.) 
magick::image_read(image[2])

table <- data.frame(html_nodes(game ,"table")[3] %>% html_table())
table[,1:3]
```
