---
title: "A Series of Tubes..."
author: "Hana Lee"
topic: "09"
layout: post
root: ../../../
output: 
  html_document: 
    css: extra.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#####1. The `xml2` R package can be used to work with xml files. Write a function, `current_weather` that accepts a 4-letter airport code (KAMW in the URL here: https://w1.weather.gov/xml/current_obs/KAMW.xml) and returns a data frame with the airport location (station ID, latitude, longitude), last update time, and current weather information (temperature, weather condition, wind speed and direction) at that airport. The `xml2` functions `read_xml`, `xml_children`, `xml_name`, and `xml_text` will be useful. Remember to handle errors and check inputs, and make sure to return a data frame with appropriate data types. 


```{r message=F, warning=F}
library(xml2)
airport.code <- "KAMW"


current_weather <- function(airport.code.4.digit){

  URL <- paste("https://w1.weather.gov/xml/current_obs/", airport.code.4.digit, ".xml", sep="")
  dat <- read_xml(URL)

want.to.find <- c(c("station_id", 
                    "latitude",
                    "longitude",
                    "observation_time",
                    "temperature_string",
                    "weather",
                    "wind_string"))

  no <- length(want.to.find)
  i <- 0
  output <- 1:no
  repeat{
    i <- i + 1
    output[i] <- xml_text(xml_find_all(dat, paste(".//", want.to.find[i], sep="")))
    if(i == no) break
  }

res <- as.data.frame(t(output))
colnames(res) <- c("station ID", 
                   "latitude", 
                   "longitude", 
                   "last update time", 
                   "temperature", 
                   "weather condition", 
                   "wind speed and direction")

if(checkmate::checkDataFrame(res)==F) stop("Your output is not a data frame")
return(res)

}
current_weather("KAMW")

```

#####2. Which HTML tags did you investigate? Describe how to format at least 3 separate pieces of a document using HTML tags.

- The entire background color can be set as lightyellow color in the "body" tag's style. In addition, the courier font can be applied for the first heading. Lastly, in one paragraph, marking some words with yellow block is available.

- This is my example:

<!DOCTYPE html>
<html>
<head>
<title>Page Title</title>
</head>
<body style="background-color:lightyellow;">

<h1 style="font-family:courier;"><i>Section 1</i></h1>
<p>This text is <mark>NOT</mark> emphasized.</p>
<h3>Subsection 1.1</h3>
<p>My <b>first</b> paragraph.</p>
<p>My 2<sup>nd</sup> paragraph.</p>

<h1 style="color:blue;"><i>Section 2</i></h1>
<p style="text-align:center;"><em>This text is <mark>emphasized.</mark></em></p>

</body>
</html>


#####3. Compile this Rmarkdown document to HTML, then open the HTML file in a web browser. Open the inspector console for your browser (Ctrl-Shift-I in Chrome, Ctrl-Shift-C in Firefox) and look at the HTML code corresponding to various parts of the document.
Answer the following questions:

- What types of tags did you find? 
    html, head, body, div, style, p, pre ,script, code, span, and so on

- How are code chunks formatted in HTML?
    tag: pre class = "r"
    tag: code class = "hljs"
  
  display: block;  
  padding: 9.5px;  
  margin: 0 0 10px;  
  font-size: 13px;  
  line-height: 1.42857143;  
  color: #333;  
  word-break: break-all;  
  word-wrap: break-word;  
  background-color: #f5f5f5;  
  border: 1px solid #ccc;  
  border-radius: 4px;  

- What differences are there in the HTML markup for R code chunks and R output blocks?

    The "span" tag is used to group inline-elements in a document for R code chunks while the R output in the R output blocks is treated as a text. In particular, in R code chunks, the "span" tag is used to group numbers, user defined R function name as keywords, and character strings within quotes as strings while the others are considered a text.
    

#####4. In R, the `rvest` package, which is part of the tidyverse, makes it (relatively) easy to pull specific pieces from structured documents. The `html_nodes` function selects nodes using either xpath or css, and additional functions such as `html_attrs`, `html_text`, and `html_table` pull information out of the markup text. Choose a Wikipedia page that has at least one image to test the `rvest` package out

```{r message=F, warning=F}
library(tidyverse)
library(rvest)
Overcast <- xml2::read_html("https://en.wikipedia.org/wiki/Overcast")

Overcast %>% 
  html_nodes("title") %>%
  html_text()

#To find and show the image file in the wiki link above 
image.url <- Overcast %>% 
  html_nodes("meta") %>% 
  html_attrs()
magick::image_read(as.vector(image.url[[7]][2]))

#Three small tables near REFERENCE sections
Overcast %>% html_nodes("table") 
Overcast %>% html_table()
```
