---
title: "A Series of Tubes..."
author: "Weiquan Luo"
topic: "09"
layout: post
root: ../../../
output: 
  html_document: 
    # css: extra.css
---

```{r, message=FALSE}
library(xml2)
library(tidyverse)
library(checkmate)
library(rvest)
```

1. The `xml2` R package can be used to work with xml files. Write a function, `current_weather` that accepts a 4-letter airport code (KAMW in the URL here: https://w1.weather.gov/xml/current_obs/KAMW.xml) and returns a data frame with the airport location (station ID, latitude, longitude), last update time, and current weather information (temperature, weather condition, wind speed and direction) at that airport. The `xml2` functions `read_xml`, `xml_children`, `xml_name`, and `xml_text` will be useful. Remember to handle errors and check inputs, and make sure to return a data frame with appropriate data types. 

```{r}
station_id <- "KAMW"
current_weather <- function(station_id){
  url <- paste0("https://w1.weather.gov/xml/current_obs/", station_id ,".xml")
  xml <- try(read_xml(url))
  checkmate::assert_class(xml, c("xml_document", "xml_node"))
  
  nodeset <- xml_children(xml)
  checkmate::assert_class(nodeset, c("xml_nodeset"))
  
  tempname <- xml_name(xml_children(xml))
  text <- lapply(tempname, function(x) xml_text(xml_find_all(nodeset, paste0("//",x)))) %>% 
    unlist() %>% 
    set_names(tempname) %>%
    as.data.frame() %>% 
    set_names(c("Info")) %>% 
    t() %>% 
    as.data.frame()
  checkmate::assert_class(text, c("data.frame"))
  checkmate::assert_true(nrow(text) == 1)
  
  weather <- text %>% select(station_id, latitude, longitude, 
                             observation_time, 
                             temperature_string, weather, wind_mph, wind_degrees)
  checkmate::assert_class(weather, c("data.frame"))
  checkmate::assert_true(nrow(weather) == 1)
  
  return(weather)
}
station_id <- "KAMW"
cw <- current_weather(station_id)
print(cw)

```

2. Which HTML tags did you investigate? Describe how to format at least 3 separate pieces of a document using HTML tags.

* HTML The class Attribute: The HTML class attribute is used to define equal styles for elements with the same class name. So, all HTML elements with the same class attribute will have the same format and style. All element can be assigned with with class attribute. 

```{.txt}
<!DOCTYPE html>
<html>
<head>
<style>
span.note {
  font-size: 120%;
  color: red;
}
</style>
</head>
<body>

<h1>My <span class="note">Important</span> Heading</h1>
<p>This is some <span class="note">important</span> text.</p>

</body>
</html>
```

* HTML Styles - CSS: Cascading Style Sheets. can be added to HTML elements in Inline, Internal, External. It is used to describes how HTML elements are to be displayed on screen, paper, or in other media. It save a lot of work by taking over some use of HTML `style` attribute

```{.txt}
<h1 style="color:blue;">This is a Blue Heading</h1>
```


* HTML Tables: the HTML has the `th` element for table header, the `tr` element for table row, the `caption`  element for caption of the table. All the element can be describes be CSS.

```{.txt}
<!DOCTYPE html>
<html>
<body>

<h2>Basic HTML Table</h2>

<table style="width:100%">
  <tr>
    <th>Firstname</th>
    <th>Lastname</th> 
    <th>Age</th>
  </tr>
  <tr>
    <td>Jill</td>
    <td>Smith</td>
    <td>50</td>
  </tr>
  <tr>
    <td>Eve</td>
    <td>Jackson</td>
    <td>94</td>
  </tr>
  <tr>
    <td>John</td>
    <td>Doe</td>
    <td>80</td>
  </tr>
</table>

</body>
</html>
```
3. Compile this Rmarkdown document to HTML, then open the HTML file in a web browser. Open the inspector console for your browser (Ctrl-Shift-I in Chrome, Ctrl-Shift-C in Firefox) and look at the HTML code corresponding to various parts of the document. <br>
Answer the following questions:

    - What types of tags did you find? 
    
    * <html>: define the whole
    * <h1>, <h4>: heading for title and author\'s name
    * <body>: main
    * <div>: division
    * <li>: list
    * <p>: paragraph
    * <ul>: I guess unit list? 
    * <pre>: parent node of the `code` node
    * <code>: code chunk
    
    - How are code chunks formatted in HTML?
    
    It use  <pre class="r"> or  <pre class="txt"> depend on the designate formate of the code chunk.

    - What differences are there in the HTML markup for R code chunks and R output blocks?
    
    * R output blocks is formated with paragrahp using <p>
    * R code chunks is formated with <pre> and <code>
    
4. In R, the `rvest` package, which is part of the tidyverse, makes it (relatively) easy to pull specific pieces from structured documents. The `html_nodes` function selects nodes using either xpath or css, and additional functions such as `html_attrs`, `html_text`, and `html_table` pull information out of the markup text.<br>
Choose a Wikipedia page that has at least one image to test the `rvest` package out

```{r}
url <- "https://en.wikipedia.org/wiki/List_of_cognitive_biases"
html <- read_html(url)
List_of_cognitive_biases <- html %>% html_nodes(".wikitable") %>% html_table() 
str(List_of_cognitive_biases)
tempname <- html %>% html_nodes(".mw-headline") %>% html_text

for (i in 1:3) assign(tempname[i], List_of_cognitive_biases[[i]])
```


