---
title: "A Series of Tubes..."
author: "Stephanie Reinders"
topic: "09"
layout: post
root: ../../../
output: 
  html_document: 
    css: extra.css
---

**Write a blog post answering the following questions and detailing the progress: **

1. The `xml2` R package can be used to work with xml files. Write a function, `current_weather` that accepts a 4-letter airport code (KAMW in the URL here: https://w1.weather.gov/xml/current_obs/KAMW.xml) and returns a data frame with the airport location (station ID, latitude, longitude), last update time, and current weather information (temperature, weather condition, wind speed and direction) at that airport. The `xml2` functions `read_xml`, `xml_children`, `xml_name`, and `xml_text` will be useful. Remember to handle errors and check inputs, and make sure to return a data frame with appropriate data types. 

```{r include=FALSE}
library(xml2)
library(tidyverse)
library(lubridate)
library(RCurl)
library(rvest)
```

```{r echo=FALSE}

current_weather <- function(airport_code){

# Change to uppercase if it is not already  
airport_code <- toupper(airport_code)

if(!is.character(airport_code)){
  warning("airport_code is not a character string")
  return(NA)
}

if(nchar(airport_code)!=4){
  warning("airport_code is not four characters")
  return(NA)
}

# Generate url and read xml data
url <- paste0("https://w1.weather.gov/xml/current_obs/", airport_code, ".xml")
w <- read_xml(url)

# Pull out the values (text or numeric) from specific xml nodes
station_id <- xml_text(xml_child(w, "station_id"))  
longitude <-xml_double(xml_child(w, "longitude"))
latitude <- xml_double(xml_child(w, "latitude"))
observation_time <- xml_text(xml_child(w,"observation_time"))
temperature <- xml_double(xml_child(w,"temp_f"))
weather_condition <- xml_text(xml_child(w,"weather"))
wind_speed <- xml_text(xml_child(w,"wind_mph"))
direction <- xml_text(xml_child(w,"wind_dir"))

df <- data.frame(station_id,longitude,latitude,observation_time,temperature,weather_condition,wind_speed,direction)  

# Reformat the observation time text
df <- df %>% 
  mutate(observation_time = gsub("Last Updated on ","",observation_time),
         observation_time = mdy_hm(observation_time,tz="US/Central"))

return(df)
}

airport_code <- "KAMW"
current_weather(airport_code)
```


2. Which HTML tags did you investigate? Describe how to format at least 3 separate pieces of a document using HTML tags.

Text can be formatted a variety of ways: 
    - We can make text <b> bold</b>. 
    - We can make text <i> italic</i>.
    - We can <mark>highlight</mark> text.

Pagraphs can be formatted differently.
  <p>This is the default paragraph style. Regardless of how many     extra spaces    or line breaks I 
  make when I type. This paragraph style will remove extra spaces and ignore my line breaks. </p>
  <pre>This is a different paragraph style. It will preserve    extra     spaces  and 
  my
  line
  breaks.</pre> 

Lists also have a variety of formatting options:

Basic list
<ul>
  <li>item 1</li>
  <li>item 2</li>
  <li>item 3</li>
</ul>  

List with open circles
<ul style="list-style-type:circle;">
  <li>item 1</li>
  <li>item 2</li>
  <li>item 3</li>
</ul> 

List with squares
<ul style="list-style-type:square;">
  <li>item 1</li>
  <li>item 2</li>
  <li>item 3</li>
</ul> 
  
List without bullets
<ul style="list-style-type:none;">
  <li>item 1</li>
  <li>item 2</li>
  <li>item 3</li>
</ul>  
  

3. Compile this Rmarkdown document to HTML, then open the HTML file in a web browser. Open the inspector console for your browser (Ctrl-Shift-I in Chrome, Ctrl-Shift-C in Firefox) and look at the HTML code corresponding to various parts of the document. <br>
Answer the following questions:

    - What types of tags did you find?
        I found all sorts of headings and paragraph tags as well as quite a few `<div> </div>` tags to denote sections. 

    - How are code chunks formatted in HTML?
    
      The tags used to display the R code are `<pre class="r"> <code class="hljs">`

    - What differences are there in the HTML markup for R code chunks and R output blocks?
    
      The tags used to display the R output blocks is the same as for the R code chucks expect it doesn't specify 'class = "r"' in the paragraph tag <pre>.
    
4. In R, the `rvest` package, which is part of the tidyverse, makes it (relatively) easy to pull specific pieces from structured documents. The `html_nodes` function selects nodes using either xpath or css, and additional functions such as `html_attrs`, `html_text`, and `html_table` pull information out of the markup text.<br>
Choose a Wikipedia page that has at least one image to test the `rvest` package out

```{r echo=FALSE}
url <- "https://en.wikipedia.org/wiki/Helen_Keller"
html <- read_html(url)
html %>% html_nodes("img") %>% .[1]
```

```{r echo=FALSE}
html %>%
  html_nodes("table") %>%
  .[[1]] %>%
  html_table()
```

