---
title: "A Series of Tubes..."
author: "Xiyuan Sun"
topic: "09"
layout: post
root: ../../../
output: 
  html_document: 
    css: extra.css
    fig_caption: yes
---

**Write a blog post answering the following questions and detailing the progress: **

1. The `xml2` R package can be used to work with xml files. Write a function, `current_weather` that accepts a 4-letter airport code (KAMW in the URL here: https://w1.weather.gov/xml/current_obs/KAMW.xml) and returns a data frame with the airport location (station ID, latitude, longitude), last update time, and current weather information (temperature, weather condition, wind speed and direction) at that airport. The `xml2` functions `read_xml`, `xml_children`, `xml_name`, and `xml_text` will be useful. Remember to handle errors and check inputs, and make sure to return a data frame with appropriate data types. 

```{r message = FALSE}
library(xml2)
library(tidyverse)
library(assertthat)
#write a function current_weather
#that accepts a 4-letter airport code
#and returns a data frame with 
#(1) the airport location (station ID, latitude, longitude)
#(2) last update time
#(3) current weather information (temperature, weather condition, wind speed and direction)

current_weather <- function(code) {
  assert_that(is.character(code), nchar(code)==4, msg="Code is not a 4 letter char")
  
  url <- paste0("https://w1.weather.gov/xml/current_obs/", code, ".xml")
  xml <- read_xml(url)
  nodeset <- xml %>% xml_children 
  name <- nodeset %>% xml_name
  content <- nodeset %>% xml_text
  dat <- as.data.frame(matrix(content, ncol = length(content), byrow = T), stringsAsFactors = F)
  colnames(dat) <- name
  res <- dat %>% dplyr::select(station_id, latitude, longitude,
    observation_time, weather, temperature_string, wind_dir, wind_mph)
  
  checkmate::checkDataFrame(res)
  return(res)
}

#test it
current_weather("KAMW")
current_weather("KSTP")


```


2. Which HTML tags did you investigate? Describe how to format at least 3 separate pieces of a document using HTML tags.

Colors

<!--html_preserve-->
<h1 style="background-color:rgb(60, 19, 110);color:Yellow;border:10px dashed #F10909">Smokey is a cat.</h1>
<!--/html_preserve-->

Table

<!--html_preserve-->
<table style="width:50%">
  <tr>
    <th>Language</th>
    <th>Interests</th>
  </tr>
  <tr>
    <td>English</td>
    <td>Natural Language Processing.</td>
  </tr>
  <tr>
    <td>Spanish</td>
    <td>Procesamiento natural del lenguaje.</td>
  </tr>
</table>
<!--/html_preserve-->


3. Compile this Rmarkdown document to HTML, then open the HTML file in a web browser. Open the inspector console for your browser (Ctrl-Shift-I in Chrome, Ctrl-Shift-C in Firefox) and look at the HTML code corresponding to various parts of the document. <br>
Answer the following questions:

    - What types of tags did you find? 
    
      Width, height of frame broader and font sizes.
      
    - How are code chunks formatted in HTML?
      
      R code chunks are with pre class="r" tags
      
      The actual text is within a class="hljs" tag

    - What differences are there in the HTML markup for R code chunks and R output blocks?
    
    output color of attaching packages
    
    
    
4. In R, the `rvest` package, which is part of the tidyverse, makes it (relatively) easy to pull specific pieces from structured documents. The `html_nodes` function selects nodes using either xpath or css, and additional functions such as `html_attrs`, `html_text`, and `html_table` pull information out of the markup text.<br>
Choose a Wikipedia page that has at least one image to test the `rvest` package out

```{r}
library(rvest)
yammie <- read_html("https://en.wikipedia.org/wiki/Yammie_Lam")

html_node(yammie,"img") %>% 
  xml_attr(attr="src") %>%
  paste0("https:",.) %>%
  magick::image_read()

html_nodes(yammie,"table")[3] %>%
  html_attr("class")

html_nodes(yammie,"table")[3] %>%
  html_table()
```






