---
title: "A Series of Tubes..."
author: "Zhenzhen Chen"
topic: "09"
layout: post
root: ../../../
output: 
  html_document: 
    #css: extra.css
---



**Write a blog post answering the following questions and detailing the progress: **


1. 
```{r}
library(tidyverse)
library(xml2)

current_weather <- function(airport){
  
  checkmate::assertCharacter(airport)
  ## read the data and select corresponding elements
  airport <- read_xml(paste0("https://w1.weather.gov/xml/current_obs/", airport, ".xml" ))
  dataname <- airport %>% xml_children() %>% xml_name() %>% .[c(7, 8, 9, 10, 14, 15, 20, 18)]
  seldata <- airport %>% xml_children() %>% xml_text %>% .[c(7, 8, 9, 10, 14, 15, 20, 18)]
  
  ## construct a data.frame
  dat <- as.data.frame(matrix(seldata, ncol = length(seldata)), stringsAsFactors = F)
  colnames(dat) <- dataname
  
  checkmate::check_data_frame(data) # check whether the output is a data.frame
  return(dat)
}

current_weather("KAMW")
current_weather("KCNC") 
```



2. Which HTML tags did you investigate? Describe how to format at least 3 separate pieces of a document using HTML tags.

The three HTML tags I investigate are 

-image: 
<img src = "https://www.uniquevenues.com/sites/uniquevenues.com/files/imagecache/2015_venue_flexslider/venues/slideshow/Central_Campus.jpg" width = "500", height = "600">

- title 
<p title = "Here is my paper">
Long long a ago, there is a little girl. 
</p>

- document
<html>
<body>

<h1> Statistical Inference </h1>
<h2> Probability distribution </h2>
<p> The first objective is to develop the first principles of statistical inference. </p>

</body>
</html>


3. Compile this Rmarkdown document to HTML, then open the HTML file in a web browser. Open the inspector console for your browser (Ctrl-Shift-I in Chrome, Ctrl-Shift-C in Firefox) and look at the HTML code corresponding to various parts of the document. <br>
Answer the following questions:
    - What types of tags did you find? 
    Background color, color , font-size 
    - How are code chunks formatted in HTML?
    <pre class="r">
    - What differences are there in the HTML markup for R code chunks and R output blocks?
    The R code chunks has class "r" under the "code" tag. The R output blocks has class "hljs" tags. 
    
4.
```{r}
library(rvest)
ggp <- read_html("https://en.wikipedia.org/wiki/Ggplot2")

read_ima <- ggp %>% html_nodes("img") %>%
   html_attr("src") %>%
   paste0("https:",.) 

ima <- knitr::include_graphics(read_ima[[1]])

```

