---
title: "It's magick!"
author: "Budi Joshua"
root: ../../../
layout: post
topic: 08
---

## Background:

Image files come in all kinds of formats. There's png, tiff, svg, pdf, just to name a few. What's the difference, and how can we work with them?

Reading: 

  - Identify online sources to read up on differences between image file formats. 

  - The `magick` package allows us to work with raster images in R. Read through the  [magick vignette](https://cran.r-project.org/web/packages/magick/vignettes/intro.html) to learn about the package's functionality.

Write a blog post answering the following questions and detailing the progress: 

1. **Describe the difference between formats png, svg, and pdf. State your sources with (working!) links (take a look at the RMarkdown cheatsheet for RStudio to learn how to make working links). Make one plot in ggplot2 and save it (using R code) in each of the three file formats you discussed. Comment on the differences you observe in their usage.**

SVG (Scalable vector graphic) image format is usually used for websites. It is suitable to be projected in devices with high pixels without suppressing image quality when compressed or stretched.   
PDF (Portable Document File) image format are suitable to be printed out and exchanged between different users. It is easy to transfer using emails or upload/download since the document size is usually small. It can be viewed either using AdobePDF or browser, therefore very wide-range of use.   
PNG (Portable Network Graphics) image format is the best in preserving quality compared to SVG and PDF, especially when there is a mixture of art and text. Therefore, the file size gets bigger as well. An interesting feature is that it can include transparency and fading effect, such like GIF.   
source: 95visual.com (https://www.95visual.com/blog/svg-pdf-jpg-png-whats-the-difference)

```{r include=FALSE, message=FALSE}
library(dplyr)
str(CO2)
library(Rmisc)

CO2.summ<- summarySE(CO2, measurevar="uptake", groupvars=c("Type","Treatment"))
```

```{r echo=FALSE}
barplot <- ggplot(CO2.summ, aes(Type, uptake, fill=Treatment)) +
  geom_bar(stat="identity", position="dodge")+
  ggtitle("CO2 uptake of grasses, cold tolerance of Echinochloa crus-galli")
barplot
```

```{r message=FALSE, include=FALSE}
ggsave("co2grass.pdf")
library("svglite")
ggsave("co2grass.svg")
ggsave("co2grass.jpeg")
```


2. **Use `magick` functionality to create an image to be used for a hex sticker.**  package `hexSticker` can help you to get started on dimensions of the sticker. **Include all code necessary to produce your sticker.** In case you are using local images, post those in a folder on **your** website and use the URL to link to them.

```{r message=FALSE, warning=FALSE}
library(magick)
library(hexSticker)
```

```{r message=FALSE}
hex<- hexagon(size=1.2, fill="#003000")

bfr <- image_read("https://joeybudi.github.io/images/breadfruit2.png") 
bfr
bfr2 <- bfr %>%
  image_scale("300") %>%
  image_crop("300x300+0+0")
bfr2
```

```{r}
bfr_sticker <- sticker(bfr2, 
                       s_width=1.2, 
                       s_height=1.2, 
                       s_x=1, 
                       s_y=1.1, 
                       p_y=0.5, 
                       package="breadfruit",
                       p_color="black",
                       h_fill="#ffffff", 
                       h_color="#028213")

bfr_sticker
```

