---
title: "It's magick!"
author: "Jing Zhao"
topic: "08"
layout: post
root: ../../../
---

Write a blog post answering the following questions and detailing the progress: 

1. **Describe the difference between formats png, svg, and pdf. State your sources with (working!) links (take a look at the RMarkdown cheatsheet for RStudio to learn how to make working links). Make one plot in ggplot2 and save it (using R code) in each of the three file formats you discussed. Comment on the differences you observe in their usage.**

I use the source to understand the different among format png, svg, and pdf [source link](https://www.95visual.com/blog/svg-pdf-jpg-png-whats-the-difference)


*SVG*
Scalable Vector Graphics (SVG), was developed to be used to represent an image and its elements.It can be open in any browser and keep image quality with either compressed or stretched. This format is suitable for web pages such as smart phone. The potential issue for using SVG is the entire object must be loaded albit you are only interested in partial object.

*PDF*
Portable Document File (PDF), is a file fomat that can be used to provide an electronimc image of text as a printed document. The link can be embedded in the document and the file size are usually smaller than other graphic files.

*PNG*
Portable Network Graphics (PNG), is an open format that could be an alternative to the GIF format, but with  better quality than GIF. It is used extensively on websites.

```{r}
library(tidyverse)
library(magick)
head(mtcars)
mtcars %>% ggplot() + geom_point(aes(x=hp,y=mpg,color=hp)) + facet_grid(~cyl)
  ggsave("mpg_cyl.pdf") +
  ggsave("mpg_cyl.png") + 
  ggsave("mpg_cyl.svg")
```


2. **Use `magick` functionality to create an image to be used for a hex sticker.**  package `hexSticker` can help you to get started on dimensions of the sticker. **Include all code necessary to produce your sticker.** In case you are using local images, post those in a folder on **your** website and use the URL to link to them.


```{r}
library(magick)
library(hexSticker)
img <- image_read("https://jeroen.github.io/images/banana.gif")
print(img)
sticker <- sticker(img, package = "Banana", s_x = 1, s_y = 1, s_width = 1, s_height = 1, h_fill = "purple")
sticker
```





