---
title: "It's magick!"
author: "Jessica Kueon"
topic: "08"
layout: post
root: ../../../
---

## Background:

Image files come in all kinds of formats. There's png, tiff, svg, pdf, just to name a few. What's the difference, and how can we work with them?

Reading: 

  - Identify online sources to read up on differences between image file formats. 

  - The `magick` package allows us to work with raster images in R. Read through the  [magick vignette](https://cran.r-project.org/web/packages/magick/vignettes/intro.html) to learn about the package's functionality.

Write a blog post answering the following questions and detailing the progress: 

1. **Describe the difference between formats png, svg, and pdf. State your sources with (working!) links (take a look at the RMarkdown cheatsheet for RStudio to learn how to make working links). Make one plot in ggplot2 and save it (using R code) in each of the three file formats you discussed. Comment on the differences you observe in their usage.**

[Click me](https://www.95visual.com/blog/svg-pdf-jpg-png-whats-the-difference)

PNG is an open, higher-quality file format even compared to GIF. More suitable for web images like logos. 

SVG is developed to be used in XML website design. It has a high pixel density and easy to edit. 

PDF is developed by Adobe, and provide an electronic image of test that looks the same as a printed document. 



```{r}

library(tidyverse)
library(survival)
head(lung)
plot <- lung %>% ggplot(aes(time, colour = factor(sex))) + geom_density()


ggsave("plot.png")
ggsave("plot.tiff")
ggsave("plot.pdf")
ggsave("plots.svg")
```
2. **Use `magick` functionality to create an image to be used for a hex sticker.**  package `hexSticker` can help you to get started on dimensions of the sticker. **Include all code necessary to produce your sticker.** In case you are using local images, post those in a folder on **your** website and use the URL to link to them.


```{r}
library(svglite)
library(magick)
library(hexSticker)

peng<- "https://i.imgur.com/uJiJz4u.png"

peng2 <- image_read('https://i.imgur.com/uJiJz4u.png') %>%
  image_trim %>% image_transparent("lightskyblue")

peng_sticker <- sticker(peng2, package = "penguin", s_x = 1, s_width = 0.8, s_height = 1, p_y = 1.5, p_color = "black", h_fill = "white")

peng_sticker
```



## Instructions:
