---
title: "It's magick!"
author: "YonghuiHuo"
topic: "08"
layout: post
root: ../../../
---

## Background:

Image files come in all kinds of formats. There's png, tiff, svg, pdf, just to name a few. What's the difference, and how can we work with them?

Reading: 

  - Identify online sources to read up on differences between image file formats. 

  - The `magick` package allows us to work with raster images in R. Read through the  [magick vignette](https://cran.r-project.org/web/packages/magick/vignettes/intro.html) to learn about the package's functionality.

Write a blog post answering the following questions and detailing the progress: 

1. **Describe the difference between formats png, svg, and pdf. State your sources with (working!) links (take a look at the RMarkdown cheatsheet for RStudio to learn how to make working links). Make one plot in ggplot2 and save it (using R code) in each of the three file formats you discussed. Comment on the differences you observe in their usage.**
* source: http://socialcompare.com/en/comparison/image-file-formats
PNG was created to improve GIF image-file format. Removing patent license issues at that time; and removing 256 colors limitation. Pros: Widely accepted format, Lossless Transparency support. Cons: More complex and larger image files can be large, Only supports web colors (RGB), Limited compatibility.
SVG is an XML based file format. It allows to create vector graphics with animation and interaction support. It can be edited with any text editor. Pros: Can be expanded infinitely without quality loss
Can be edited with a text editor. Cons:	Support growing but still limited, Not intended for print.
PDF is a file format used to present documents in a manner independent of application software, hardware, and operating systems. Each PDF file encapsulates a complete description of a fixed-layout flat document, including the text, fonts, graphics, and other information needed to display it. Pros: Lossless
Protects intellectual property. Maintains printed format. Cons:Longer browser loading times
Non-editable content. Not great for complex graphics printing. Not really useful as a graphic image.

From the plot saved in my computer, it is obvious that pdf is the most clearest while also take more space.
```{r}
library(tidyverse)
library(magick)
mydata=diamonds[sample(nrow(diamonds), 1000), ]%>%filter(!color%in%c("J", "I"))
b=mydata%>%ggplot(aes(x=cut, fill=cut))+geom_bar(aes(weight=depth), width = 1)+
  coord_polar(theta = "x", start = 0, direction = -1)
ggsave(file='polar.svg')
ggsave(file='polar.pdf')
ggsave(file='polar.png')
```

2. **Use `magick` functionality to create an image to be used for a hex sticker.**  package `hexSticker` can help you to get started on dimensions of the sticker. **Include all code necessary to produce your sticker.** In case you are using local images, post those in a folder on **your** website and use the URL to link to them.
```{r}
library("hexSticker")
cat <- image_read("https://jpninfo.com/wp-content/uploads/2015/05/japanese-cartoon-1.jpg")
st <- sticker(cat, package = "cats", s_x = 1, s_y = 1, s_width = 1, s_height = 1, h_fill = "gray")
st
```
